\begin{thebibliography}{}
%% Introduction %%

\bibitem{simple_background_subtraction} Y. Benezeth, P.-M. Jodoin, B. Emile, H. Laurent \& C. Rosenberger. October 2012. \emph{Comparative Study of Background Subtraction Algorithms}, pp. 5-6.

\bibitem{jog_halbe} Aditi Job \& Shirish Halbe. October 2012. \emph{Multiple Objects Tracking using CAMshift Algorithm in Open CV}, pp. 41-46.

\bibitem{gellert} Gellert, A. \& Vintan, L., 2006, \emph{Person Movement Prediction Using Hidden Markov Models}, Computer Science Department, University of Sibiu, \url{http://webspace.ulbsibiu.ro/arpad.gellert/html/SIC_HMM.pdf}.

\bibitem{ashbrook} Ashbrook, D. \& Starner, T., \emph{Using GPS to Learn Significant Locations and Predict Movement Across Multiple Users}, Georgia Institute of Technology, \url{http://www.cc.gatech.edu/~thad/p/journal/using-gps-to-learn-significant-locations.pdf}.

%% Analysis %%

\bibitem{bhatia} Bhatia, N., 2010. \emph{Survey of Nearest Neighbor Techniques}, p. 303. \url{http://arxiv.org/ftp/arxiv/papers/1007/1007.0085.pdf}

%% Design %%

\bibitem{background_subtraction_1} Massimo Piccardi. 2004. \emph{Background subtraction techniques: a review}, p. 1.

\bibitem{running_average_approach_1} Mohamad Hoseyn Sigari, Naser Mozayani \& Hamid Reza Pourreza. February 2008. \emph{Fuzzy Running Average and Fuzzy Background Subtraction: Concepts and Application}, p. 1.

\bibitem{blur_1} Herman Cheng, Zhicong Huang \& Mark Kumimoto. Spring 2006. \emph{Final Project Report - Image Processing Techniques}, pp. 2-4.

\bibitem{grayscale_1} Matt Siber. Fall 2005. \emph{Resolution and File Size}, p. 1.

\bibitem{threshold_1} Brian Lovell \emph{Thresholding Techniques}. Spring 2003.

\bibitem{dilation_1} R. Fisher, S. Perkins, A. Walker \& E. Wolfart. 2003. \emph{Dilation}.

\bibitem{erosion_1} R. Fisher, S. Perkins, A. Walker \& E. Wolfart. 2003. \emph{Erosion}.

\bibitem{bounding_box_1} Dr. Nicolas Pronost. \emph{Introduction to Image Processing}, p. 9.

\bibitem{histogram_1} Ahmed Elgammal. Spring 2008. \emph{Histograms of Digital Images}.

%% Implementation %%

\bibitem{opencv_1} OpenCV. \url{http://opencv.org/about.html}


%% Evaluation %%

%% Collaboration and Process%%

\bibitem{scrum} K. Schwaber. November 2009. \emph{Agile Project Management with Scrum}.

\bibitem{project_management_approches} Pekka Abrahamsson, Outi Salo, Jussi Ronkainen, Juhani Warsta. VTT Publications 478. 2002. \emph{Agile Software Development Methods} , p.98.

\bibitem{agile_project_management} Alistair Cockburn and Jim Highsmith.\emph{Agile software development, the people factor.}, Computer 34, no. 11 (2001): 131-133.

\bibitem{jour_fixe} Gerold Patzak, Günter Rattay. 2011. \emph{Guideline for the Management of Projects}, p.415

\bibitem{trust} Nikki Panteli, Robert Tucker, 2009. \emph{Power and Trust in Global Virtual Teams}.

%% Discussion %%

%% Conclusion %%

\end{thebibliography}